Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-20 PAPER.tex
edited plot and caption of Fig 25 - null test

\begin{figure*}
	\centering
	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
	\caption{Power spectrum results (with $2\sigma$ errors) for two null tests, where a jackknife is taken along the LST axis (left) and baseline axis (right). The results shown are unweighted. The gray shaded region is the estimated $2\sigma$ theoretical noise limit given the parameters of each test. We find that there are no significant systematics that differ between the two tests, though the $k$-dependence of the errors suggest that we are dominated by residual foregrounds near the horizon.}
	\label{fig:null}
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the LST axis (top left), baseline axis (top right), and even/odd Julian date axis (bottom). The results shown are unweighted. The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test. We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to thermal noise squaring). All three tests are dominated by residual foregrounds at $k$-values near the horizon, which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
	\label{fig:null}
\end{figure*}
